A molecular dynamics study of the solvation of CO\textsubscript{2}, water, and some organic compounds in the ionic liquids [emim][B(CN)\textsubscript{4}] and [emim][NTf\textsubscript{2}]

### 2018-02-19 ionic_liquids.tex
working version

\section{Introduction}
State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results.

@@

@@

In this section, we present results of preliminary simulations, which aimed at setting up a computational efficient protocol for the ionic liquids studied here.  As alternatives to standard approaches, in this work we assess the possibility of modeling the ions as rigid bodies and employing the DSF method for calculating the electrostatic interactions.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:scheme}
\end{figure}

rigid-body configurations: We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case.

@@

\begin{figure*}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{koller}%
}
\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{batista}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{Liu}%
}
\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=.4\linewidth]{Weber}%
}
\caption{}
\label{}
\end{figure*}

\begin{figure}
\centering
\subfloat[text for the first subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{Ludwig}%
}

\subfloat[text for the second subfigure\label{sfig:testa}]{%
  \includegraphics[width=\linewidth]{Ludwig_anion}%
}
\caption{}
\label{}
\end{figure}

@@

\bibliography{mybibfile}
%\begin{equation}
%\begin{split}
%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
%\end{split}
%\end{equation}
\end{document}

>>>>

\section{Introduction}
State the objectives of the work and provide an adequate background, avoiding a detailed literature survey or a summary of the results. foreseeable future

@@

Among the force fields described in Sec.~\ref{sec:force_field_il}, only in Ref.~\citenum{Koller_2012} one can find the atomic coordinates of a minimum energy configuration obtained in an \textit{ab-initio} simulation. For the other models, we employ the tool \textit{build} of PLAYMOL, which enables to specify the geometric data of each model: bond and angle lengths and dihedral angles, from which PLAYMOL automatically determines the Cartesian coordinates. We first carried out simulations of the isolated ion pairs in order to obtain the minimum energy configurations with respect to the corresponding (classical) model for each case. Then, we obtain configurations of minimum energy with respect to the corresponding classical model. For this, we perform a series of MD simulations of each cation-anion pair. These simulations were performed in a cubic box of length L = 50 {\AA}. Initially, a short DM NVT with a time-step of 0.1 fs, followed by an equilibration using $\Delta t$ = 0.5 fs and, finally, we minimize the energy using 1 fs in a process of ``quenching'', in which the temperature is gradually reduce until reaching a value close to 0 K, for which we employ the Nos\'{e}-Hoover thermostat~\cite{Martyna1992}.

@@

In this section, we present results of preliminary simulations, which aimed at setting up a (more) computationally efficient protocol for the ionic liquids studied here. As alternatives to standard approaches, we assess the possibility of modeling the ions as rigid bodies and employing the DSF method~\cite{Fennell2006} for calculating the electrostatic interactions. For that, we compare the simulated properties of density and radial distribution functions to that obtained when considering the ions as flexible molecules and the Ewald method for the Coulombic interactions.

For the determining the initial configuration to specify for the rigid bodies we performed a preliminary study of the dihedrals in the ethyl group of [emim]$^{+}$, as we consider that its flexibility  may introduce a more significant conformational change in the cation. Small anions are usually simulated as rigid bodies. The nomenclature of the atoms are shown in Fig.~\ref{fig:atoms_name}. In the \textit{united-atoms} version of [emim]$^{+}$,  the nomenclature is identical, but hydrogens ranging from H4 to H11 are eliminated.

Using the software TRAVIS~\cite{Brehm_2011}, for each model we obtain the combined distribution function for the angles of the dihedrals C1-N2-C5-C6 and C2-N2-C5-C6 sampled in NPT simulations of 250 ion pairs. We chose this analysis, in place of individual histograms, as it provides simultaneously rigidity of the ring. In Figure we present the results for each model, together withe the color scale associated to the histograms.

A first inspection of Fig.~\ref{fig:dihedrals}, reveals a similar behavior of the models of Refs.~\cite{Koller_2012} and Liu.~\cite{Liu_2014}. This was previsible

\begin{figure}
\centering
\includegraphics[width=\linewidth]{ions_paper.pdf}
\caption{[emim]$^{+}$ [B(CN)\textsubscript{4}]$^{-}$ [Tf\textsubscript{2}N]$^{-}$.}
\label{fig:atoms_name}
\end{figure}

%\begin{figure*}
%\centering
%\subfloat[text for the first subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{koller}%
%}
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{batista}%
%}
%
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{Liu}%
%}
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=.4\linewidth]{Weber}%
%}
%\caption{ggggg}
%\label{fig:dihedrals}
%\end{figure*}

%\begin{figure}
%\centering
%\subfloat[text for the first subfigure\label{sfig:testa}]{%
%  \includegraphics[width=\linewidth]{Ludwig}%
%}
%
%\subfloat[text for the second subfigure\label{sfig:testa}]{%
%  \includegraphics[width=\linewidth]{Ludwig_anion}%
%}
%\caption{}
%\label{}
%\end{figure}

@@

@@

\bibliography{mybibfile}

\end{document}
%\begin{equation}
%\begin{split}
%\Delta G_{\text{sim}} - k_b T \ln \left( \frac{V^{\ast}}{V_1} \right) &= k_b T \ln \left(\frac{P_s}{x_s} \frac{1}{\tilde{\rho}_{\scaleto{LI}{4pt}}} \right) \\
%&= k_b T \ln \left( \frac{K_s}{\tilde{\rho}_{\scaleto{LI}{4pt}} R T} \right),
%\end{split}
%\end{equation}
